\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[normalem]{ulem}

\hypersetup{colorlinks=true, linkcolor=blue!50!black, urlcolor=blue!50!black, citecolor=blue!50!black}

\title{Basal mixing model: forward dynamics and sampling strategies}
\author{BasalMixing repository}
\date{\today}

\newcommand{\Kr}{\ensuremath{{}^{81}\mathrm{Kr}}}
\newcommand{\Ar}{\ensuremath{\delta^{40}\mathrm{Ar}_{\mathrm{atm}}}}
\newcommand{\tzero}{\ensuremath{t_{0}}}
\newcommand{\tend}{\ensuremath{t_{\mathrm{end}}}}
\newcommand{\teq}{\ensuremath{t_{\mathrm{eq}}}}
\newcommand{\told}{\ensuremath{t_{\mathrm{old}}}}
\newcommand{\code}[1]{\texttt{#1}}

\begin{document}

\maketitle

\begin{abstract}
\noindent
This document describes the 1-D basal mixing model used in the BasalMixing
repository to interpret deep-ice \Kr{} and \Ar{} measurements at GISP2, and
the Markov-chain Monte Carlo (MCMC) strategy used to jointly infer the
mixing parameters and the time \tzero{} of glacial inception at the GISP2
site. The recommended strategy (\code{:sampled}) treats \tzero{} as a
physical parameter of interest with a uniform prior on $[-3000, -700]$~kyr,
where the bounds come from the geological window of first Greenland Ice
Sheet (GrIS) glaciation ($\sim$2700~kyr ago) and the lower bound on basal
ice age implied by \Kr{} measurements assuming no mixing
($\sim$700~kyr).\footnote{Sign convention: \tzero{} is reported in signed
kyr (negative $=$ past); $\tzero=0$ is the present day.} Two earlier
strategies (\code{:profile} and \code{:marginal}) are retained for
comparison and historical context; they are not the recommended treatment.
\end{abstract}

\tableofcontents

\section{The basal mixing model}
\label{sec:model}

\subsection{Physical setting}

GISP2 retrieves ice from the bottom of the Greenland Ice Sheet. The deepest
$\sim$13~m of the core sits above the bedrock and, unlike the rest of the
column, is thought to have been mechanically and diffusively mixed with
material below. Specifically: above $z=z_{\mathrm{lim}}\approx 3040\,\mathrm{m}$
the ice is treated as undisturbed (``clean'' ice); below $z_{\mathrm{lim}}$,
ice is increasingly contaminated by debris-rich (``dirty'') material that
acts as a sink/source for the tracers we measure. The model treats this lower
layer as a 1-D advection--diffusion column extending to a fixed bedrock at
$z_{\mathrm{bed}}=3053.44\,\mathrm{m}$.

\subsection{State variables and grid}

The model carries two state variables at every cell centre $z_j$ in a finite-volume
discretization:

\begin{itemize}
  \item $c_{81}(z, t)$: relative \Kr{} concentration, dimensionless. Initialized
        to 1 at $t=0$ (modern abundance) at every depth.
  \item $c_{40}(z, t)$: \Ar{} concentration, in $\mathrm{cc}\,\mathrm{m}^{-3}$.
        Initialized to the modern equilibrium value
        $A_{40}^{0} = (100\,\mathrm{cm})^{3}\cdot a_{\mathrm{tac}}\cdot
         f_{\mathrm{atm}} \approx 8000\,\mathrm{cc/m^{3}}$,
        where $a_{\mathrm{tac}}=0.08$ is the typical air content and
        $f_{\mathrm{atm}}=0.00934$ is the present-day atmospheric \Ar{} volume
        fraction.
\end{itemize}

The model integrates the forward dynamics from glacial inception at \tzero{}
up to the present day $\tend = 0$. The internal time variable used by the
integrator is the positive elapsed time $\tau = t - \tzero \in [0,\,
|\tzero|]$, advanced with a forward Euler step $d\tau=0.2\,\mathrm{kyr}$ (with
an automatic retry at $d\tau/2$ if the integrator produces non-physical,
negative concentrations). The dynamics are autonomous in $\tau$, so the only
information the integrator needs about absolute time is the total duration
$|\tzero|$.

\subsection{Mixing rate profile}

The depth-dependent mixing rate is parameterised by two values
$m_{\mathrm{clean}}$ and $m_{\mathrm{dirty}} = f_{\mathrm{dirty}}\,m_{\mathrm{clean}}$
joined by a smooth transition of thickness $\delta$ centred at
$z_{\mathrm{lim}}$. Using $w_1$ and $w_2$ for the two tanh-shaped step functions,
\begin{align}
w_1(z) &= \tfrac{1}{2}\!\left(1 + \tanh\!\big(\tfrac{\beta}{\delta}(z - z_{\mathrm{lim}})\big)\right), \\
w_2(z) &= \tfrac{1}{2}\!\left(1 + \tanh\!\big(\tfrac{\beta}{\delta}(z - z_{\mathrm{lim}} - \delta)\big)\right), \\
\Phi(z) &= m_{\mathrm{dirty}}\,w_1(z)\,w_2(z) + m_{\mathrm{clean}}\,w_1(z)\,(1 - w_2(z)),
\end{align}
with sharpness $\beta=50$ (essentially a step on the discretisation scale).
So $\Phi=0$ in clean ice, $\approx m_{\mathrm{clean}}$ in the transition zone of
width $\delta$, and $\approx m_{\mathrm{dirty}}$ in the dirty zone below.

The diffusivity is $D(z) = \Phi(z)\,L_{\mathrm{ref}}$ with $L_{\mathrm{ref}}=1\,\mathrm{m}$
treated as a reference length (it just rescales $m_{\mathrm{clean}}$; we keep
$L_{\mathrm{ref}}=1$ and let $m_{\mathrm{clean}}$ carry the magnitude).

\subsection{Governing equations}

The continuum dynamics of $c\in\{c_{81}, c_{40}\}$ are
\begin{equation}
\frac{\partial c}{\partial \tau} = \frac{\partial}{\partial z}\!\left(D(z)\,\frac{\partial c}{\partial z}\right) + S_c(z, \tau),
\label{eq:pde}
\end{equation}
discretised cell-centre to cell-centre, with $\tau$ the positive elapsed time
since inception. The source/sink term $S_c$ differs by tracer:

\begin{itemize}
  \item For \Kr{}, $S_{81}(z, \tau) = -\lambda\, c_{81}(z, \tau)$ with
        $\lambda = \ln 2 / t_{1/2}$ and $t_{1/2}=229\,\mathrm{kyr}$, except in
        the clean-ice cells for elapsed times $\tau > \told$, where the decay
        term is switched off. Physically, $\told$ is the residence time of
        the clean ice column above the mixing zone: ice older than $\told$
        is assumed to have been flushed out by ice flow, so its \Kr{} clock
        is capped at $\told$.
  \item For \Ar{}, $S_{40} = 0$ in the interior; at the bedrock cell only,
        a flux $F_{40}$ is added: $S_{40}(z_{\mathrm{bed}}, \tau) =
        F_{40}/\Delta z_{\mathrm{bed}}$.
\end{itemize}

The observable quantities derived from the state are
\begin{align}
\tau_{81}(z, \tau) &= -\,t_{1/2}\,\log_2\!\big(c_{81}(z, \tau)\big),
 \qquad \text{Kr-81 closed-system age, kyr,} \\
\delta^{40}\mathrm{Ar}_{\mathrm{atm}}(z, \tau) &= 1000\,\left(\frac{c_{40}(z,\tau)}{A_{40}^{0}} - 1\right) - 0.066\,\told,
 \qquad \text{$\delta^{40}\mathrm{Ar}$, \textperthousand},
\end{align}
where the $-0.066\,\told$ term corrects for atmospheric \Ar{} drift over the
residence time of the clean column (Bender et al.\ 2010).

\subsection{Parameters}

The six sampled parameters and the two fixed observation-noise scales are:

\begin{center}
\small
\begin{tabular}{lllp{4.5cm}l}
\toprule
Symbol & Meaning & Units & Prior & Code name \\
\midrule
$\delta$ & transition-zone thickness & m & $\mathrm{Uniform}(0.3,\,2.0)$ & \code{delta} \\
$m_{\mathrm{clean}}$ & mixing rate in transition zone & m/kyr & $\mathrm{Normal}(0.03,\,0.002)$ trunc.\ $\geq 0$ & \code{m\_clean} \\
$f_{\mathrm{dirty}}$ & dirty-to-clean mixing-rate ratio & --- & $\mathrm{Uniform}(4.0,\,6.5)$ & \code{f\_dirty} \\
$\told$ & clean-column residence time & kyr & $\mathrm{Normal}(250,\,25)$ trunc.\ $\geq 0$ & \code{t\_old} \\
$F_{40}$ & bedrock \Ar{} source flux & cc/m$^2$/kyr & $\mathrm{Uniform}(0.004,\,0.007)$ & \code{F\_ar40} \\
$\tzero$ & glacial inception time & kyr (signed) & $\mathrm{Uniform}(-3000,\,-700)$ & \code{t\_0} \\
\midrule
$\sigma_{81}$ & \Kr{} age obs.\ noise (\emph{fixed}) & kyr & 30 & \code{$\sigma$\_k81} \\
$\sigma_{40}$ & $\delta^{40}\mathrm{Ar}$ obs.\ noise (\emph{fixed}) & \textperthousand & 0.03 & \code{$\sigma$\_dar40} \\
\bottomrule
\end{tabular}
\end{center}

The choice to fix $\sigma_{81}$ and $\sigma_{40}$ rather than place priors on
them was made to improve sampling efficiency. Both values are close to the
analytical errors of the measurements; relaxing them to half-Cauchy or
exponential priors is a minor change to the model if needed.

\subsection{Observations}

The model is compared against two data sets, both at observation depths
$z_i$ corresponding to specific GISP2 ice samples:

\begin{itemize}
  \item Three \Kr{} closed-system ages, $\tau_{81}^{\mathrm{obs}}$, at depths
        $3045$--$3050\,\mathrm{m}$ (typically reported as ages of $577$, $649$, and
        $714\,\mathrm{kyr}$).
  \item Ten \Ar{} measurements from Bender et al.\ (2010), spanning depths
        $3036.5$ to $3052.4\,\mathrm{m}$, with values rising from
        $\sim 0$ \textperthousand{} in the clean zone to
        $\sim 0.5$ \textperthousand{} near bedrock.
\end{itemize}

For depths between cell centres the model predictions are linearly
interpolated. Both data sets are assumed to be independent Gaussian
observations of the corresponding model quantities at the depths in question.

\section{The likelihood and the inception-time problem}
\label{sec:tzero}

Given parameters $\theta = (\delta, m_{\mathrm{clean}}, f_{\mathrm{dirty}},
\told, F_{40})$ and an inception time \tzero{}, the model integrates over
the elapsed duration $|\tzero|$ to produce present-day predictions
$\hat{\tau}_{81}(z_i;\theta,\tzero)$ and
$\widehat{\delta^{40}\mathrm{Ar}}(z_j;\theta,\tzero)$ at the observation
depths $z_i, z_j$. Conditional on $\theta$ and \tzero{}, the log-likelihood
is the usual Gaussian:
\begin{equation}
\log L(\theta, \tzero \mid \mathbf{y}) = -\tfrac{1}{2\sigma_{81}^2}\sum_{i}\!\left(\hat{\tau}_{81}(z_i;\theta,\tzero) - y_i^{\,81}\right)^{2}
- \tfrac{1}{2\sigma_{40}^2}\sum_{j}\!\left(\widehat{\delta^{40}\mathrm{Ar}}(z_j;\theta,\tzero) - y_j^{\,40}\right)^{2} + C,
\label{eq:loglik}
\end{equation}
where $C$ collects $\theta$- and \tzero{}-independent normalising constants.

The inference problem is to recover the joint posterior on $(\theta,
\tzero)$ given the GISP2 data \textbf{y}.

\paragraph{Physical bounds on \tzero{}.}
Two independent lines of evidence bracket \tzero{}:
\begin{itemize}
  \item \emph{Upper bound ($\tzero \geq -3000$~kyr):} Greenland was
        essentially ice-free before $\sim$2700~kyr ago. Inception of the
        GrIS at the summit cannot have occurred earlier than the onset of
        large-scale Northern-Hemisphere glaciation, which the geological
        record places no earlier than the late Pliocene.
  \item \emph{Lower bound ($\tzero \leq -700$~kyr):} the deepest \Kr{}
        sample carries a closed-system age of $\sim$714~kyr. Treated as a
        no-mixing model (i.e.\ as the in-situ \Kr{} clock without any
        rejuvenation from below), that age is a lower bound on how long the
        basal ice has been sitting at the summit. Any mixing only \emph{adds}
        atmospheric-fresh \Kr{} from above, so the true ice age must be at
        least that old.
\end{itemize}
These two bounds motivate the prior $\tzero \sim \mathrm{Uniform}(-3000,
-700)$~kyr used in the recommended (\code{:sampled}) inference.

\paragraph{Data-constraint structure.}
The data weakly constrain \tzero{} from \emph{within} its prior window. The
basal mixing system reaches an effective equilibrium on timescales
$\teq(\theta)\sim 1\,000$~kyr or less, after which the present-day
predictions are nearly independent of how much longer the system has been
running. Two inception times $|\tzero^{(1)}|, |\tzero^{(2)}| > \teq(\theta)$
produce essentially identical predictions and identical likelihoods. This
saturation is the central feature of the inference and explains why the
posterior on \tzero{} is wide: the data alone cannot tell us that the GrIS
incepted at $-2300$ vs.\ $-1500$~kyr if both durations comfortably exceed
the equilibration time. What \emph{can} be ruled out is inception times
shorter than $\teq$, where the system has not yet relaxed.

\section{Sampling strategies}
\label{sec:strategies}

The repository implements three strategies, selectable by the
\code{model\_kind} variable at the top of
\code{run\_basalmixing\_ensemble.jl}. All three use the same affine-invariant
ensemble sampler (\code{Emcee}; Goodman \& Weare 2010) with 32 walkers, so
their wall-clock costs are directly comparable per integration of the forward
model.

The recommended strategy is \code{:sampled}. The other two
(\code{:profile} and \code{:marginal}) predate the present framing and are
retained for diagnostic comparison; their limitations are discussed below.

\subsection{\code{:sampled} --- joint $(\theta, \tzero)$ posterior \emph{(recommended)}}

\paragraph{What it does.}
Treat \tzero{} as one of the model's physical parameters, with the prior
$\tzero \sim \mathrm{Uniform}(-3000, -700)$~kyr motivated in
Section~\ref{sec:tzero}. For each $(\theta, \tzero)$ proposal, run the
forward model once over elapsed duration $|\tzero|$ and evaluate
(\ref{eq:loglik}) at the present-day endpoint.

\paragraph{Assumptions.}
\begin{itemize}
  \item \tzero{} is a meaningful physical quantity --- the time of glacial
        inception at the GISP2 site --- about which we have prior
        information from independent geological and isotopic constraints.
  \item The comparison time is the present day; the integration finishes
        exactly there.
\end{itemize}

\paragraph{What you get out.}
A proper joint Bayesian posterior on $(\theta, \tzero)$. The marginal on
$\theta$ accounts for uncertainty in \tzero{} by averaging; the marginal on
\tzero{} is the full inference about inception time given the data
\emph{and} the physical bounds.

\paragraph{Pros and cons.}
This is the appropriate Bayesian treatment given that we have meaningful
prior information about \tzero{} and care about its posterior. The
6-dimensional chain mixes well under \code{Emcee} (acceptance $\approx$
0.24 in test runs at 32 walkers, 500 iterations), with wall-clock per
sample governed by the mean of $|\tzero|$ across the prior.

The posterior on \tzero{} is honestly wide because the data have weak
post-equilibration power, but the width is now physically interpretable:
it represents how much the data narrow the prior window, not an artefact
of an arbitrary upper integration bound (see the discussion of
\code{:sampled-with-elapsed-time-prior} below for the previous, deprecated
framing).

\subsection{\code{:profile} --- profile likelihood \emph{(diagnostic only)}}

\paragraph{What it does.}
For every parameter proposal $\theta$, integrate the forward model from
elapsed time $\tau=0$ to a fixed upper bound $\tau_1=3000\,\mathrm{kyr}$ on
a 1-kyr grid. At each grid point compute the log-likelihood as if that
$\tau$ were the duration $|\tzero|$. Select the elapsed time that maximises
the likelihood:
\begin{equation}
\tau^{\star}(\theta) = \arg\max_{\tau}\log L(\theta, \tau \mid \mathbf{y}),
\end{equation}
and use $\log L^{\star}(\theta) = \log L(\theta, \tau^{\star} \mid \mathbf{y})$
as the contribution to the MCMC log-posterior. The chain reports
$\tzero := -\tau^{\star}(\theta)$ as a derived (non-sampled) quantity for
naming consistency with \code{:sampled}.

\paragraph{Assumptions.}
\begin{itemize}
  \item No prior on \tzero{}.
  \item The ``correct'' \tzero{} for each $\theta$ is treated as a
        deterministic function of $\theta$, chosen to make the data fit best.
\end{itemize}

\paragraph{What you get out.}
A posterior on $\theta$ from a non-standard (non-Bayesian) likelihood: the
\emph{profile likelihood} $L^{\star}(\theta)$. The reported $\tzero$ per
chain sample is a point optimum, not a sample from a posterior.

\paragraph{Pros and cons.}
Computationally efficient (the inner integration can early-terminate once
predicted ages exceed the range of interest). \textit{However:} the
posterior on $\theta$ is biased --- it over-credits each $\theta$ for the
best $\tzero$ available rather than averaging the data's support over
plausible \tzero{}. The reported $\tzero$ ``posterior'' is a histogram of
point optima with no probability-distribution interpretation. The prior
information on \tzero{} ($-3000 \leq \tzero \leq -700$~kyr) is not used.

\subsection{\code{:marginal} --- elapsed time as a nuisance parameter \emph{(deprecated)}}
\label{sec:marginal}

\paragraph{Historical context.}
The \code{:marginal} strategy was developed under an earlier framing in
which the integration duration was treated as a nuisance parameter with no
independent physical interpretation. In that framing, the goal was to
infer $\theta$ alone, marginalising the duration out of the likelihood:
\begin{equation}
\log p(\mathbf{y} \mid \theta) \;=\; \log\!\int_{0}^{\tau_1}\!\! L(\theta, \tau \mid \mathbf{y})\,p(\tau)\,d\tau,
\label{eq:marginal-loglik}
\end{equation}
with a uniform prior $p(\tau) = 1/\tau_1$ on $[0, \tau_1]$. Numerically the
integral is evaluated as a trapezoidal sum on the 1-kyr prediction grid:
\begin{equation}
\log p(\mathbf{y} \mid \theta) \;\approx\; \log\!\left(\sum_{k}\exp\!\big(\log L(\theta, \tau_k)\big)\,\Delta \tau\right),
\label{eq:marginal-trapz}
\end{equation}
computed via the standard \code{logsumexp} trick to avoid underflow. An
online equilibration check (compare predicted observation vectors $W=100$
slices apart; declare equilibrium when both \Kr{} and \Ar{} predictions
have moved less than $\sim 1\%$ of the corresponding observation noise)
allows the integrator to skip the post-equilibration tail:
\begin{equation}
\log p(\mathbf{y} \mid \theta) \;\approx\; \log\!\left(\sum_{k \leq k_{\mathrm{eq}}}\!\exp\!\big(\log L(\theta, \tau_k)\big)\,\Delta \tau \;+\; (\tau_1 - \tau_{\mathrm{eq}})\,\exp\!\big(\log L_{\mathrm{eq}}\big)\right).
\label{eq:marginal-eq}
\end{equation}

\paragraph{Why it is no longer recommended.}
The marginal-likelihood framing required \tzero{} to be a nuisance
parameter with no independent prior information --- a stance that we no
longer hold. With the physical bounds derived in Section~\ref{sec:tzero},
\tzero{} carries a meaningful prior of width $2300$~kyr, and its posterior
is a quantity we care about (it tells us when the GrIS incepted at the
summit). Two specific failure modes of \code{:marginal} under the present
framing:

\begin{itemize}
  \item \emph{The prior on \tzero{} is discarded.} Equation
        (\ref{eq:marginal-loglik}) integrates against a uniform prior on
        the elapsed-time variable $[0, \tau_1=3000]$~kyr, which is not the
        same as the physical prior $\tzero \sim
        \mathrm{Uniform}(-3000, -700)$. Inception times shorter than
        700~kyr (excluded by the \Kr{} no-mixing argument) are still given
        weight in the integrand.
  \item \emph{The posterior on \tzero{} is no longer in the chain.} A
        post-hoc reconstruction $p(\tzero \mid \mathbf{y}) \propto
        N^{-1}\sum_s L(\theta^{(s)}, \tzero) / Z(\theta^{(s)})$ averages
        per-slice likelihood curves over the marginalised-$\theta$ chain.
        It is a valid summary of what the data say about \tzero{} under
        the uniform-on-elapsed-time prior, but it does not correctly
        incorporate the physical prior either, and it requires re-running
        the forward model at every chain draw to recover.
\end{itemize}

\paragraph{When to still use it.}
For sensitivity checks: comparing the \code{:sampled} posterior on $\theta$
against the \code{:marginal} posterior under a deliberately permissive
prior tells you how much the physical prior is doing. They should agree
broadly on the well-identified parameters ($m_{\mathrm{clean}}$, \told{}); a
large disagreement on $f_{\mathrm{dirty}}$, $\delta$, or $F_{40}$ would
flag a posterior strongly shaped by the \tzero{} prior, which is worth
knowing.

\subsection{Comparison summary}

\begin{center}
\small
\begin{tabular}{lcccc}
\toprule
& \tzero{} treatment & prior on \tzero{} & posterior on \tzero{} & status \\
\midrule
\code{:sampled}  & sampled parameter & Uniform$(-3000,-700)$ & in chain & recommended \\
\code{:profile}  & point optimum     & none                  & histogram of optima & diagnostic \\
\code{:marginal} & integrated out    & Uniform$(0, 3000)$ on $\tau$ & post-hoc reconstruction & deprecated \\
\bottomrule
\end{tabular}
\end{center}

\section{Practical considerations}

\subsection{Sampler and threading}

All three model kinds use Emcee with 32 walkers and 500 iterations
($\,32\times500=16\,000$ likelihood evaluations). Emcee is appropriate here
because the posterior is moderately multimodal and the forward model is not
differentiable in a way that supports gradient-based samplers (it has a
\code{try/catch} on \code{DomainError} and mutates buffers, breaking
\code{ForwardDiff}).

Threading: each thread owns its own \code{BasalMixingModel} object, allocated
to length \code{Threads.maxthreadid()} to accommodate Julia's interactive
threads in newer versions.

\subsection{Numerical robustness}

The forward Euler integrator at $\Delta \tau=0.2\,\mathrm{kyr}$ is marginally
stable; for some proposals the explicit step overshoots and produces
non-positive concentrations, raising \code{DomainError} in
\code{concentration\_to\_age}. The forward function catches these and reports
failure; the \code{@model} retries once at $\Delta \tau/2$ before giving up
and attaching a vanishingly small likelihood.

\subsection{Outputs and reproducibility}

Each ensemble run writes a snapshot to
\code{results/emcee-chain-<model\_kind>.jld2}, containing the chain, the data
DataFrames, the depth grid, the priors, the sampler and the model kind. The
plotting helpers (\code{plot\_basalmixing\_ensemble.jl}) load this snapshot
and re-derive figures, switching the MAP best-fit re-run on the recorded
\code{model\_kind}. For \code{:sampled} chains the best-fit re-run
integrates exactly from \tzero{} to \tend{} (no extrapolation past the
inference endpoint); for \code{:profile} and \code{:marginal} it runs the
full $0 \to \tau_1$ dense grid and annotates the argmin slice.

\section*{References}

\begin{itemize}[leftmargin=*]
  \item Bender, M.~L. et al.\ ``The Contemporary Degassing Rate of $^{40}$Ar
        from the Solid Earth,'' \textit{PNAS} 105 (24), 8232--8237 (2008);
        and the GISP2 measurements used here, archived with the Bender 2010
        data set in this repository.
  \item Goodman, J.\ and Weare, J.\ ``Ensemble Samplers with Affine
        Invariance,'' \textit{Comm.\ App.\ Math.\ Comp.\ Sci.} 5, 65--80 (2010).
  \item Vihola, M.\ ``Robust adaptive Metropolis algorithm with coerced
        acceptance rate,'' \textit{Stat.\ Comput.} 22, 997--1008 (2012).
\end{itemize}

\end{document}
